Mapping the characteristics of small-scale agricultural systems at national extents using small sat data and an active learning approach

### 2021-02-24 inst/manuscript/manuscript.Rmd
Discussion drafted through error sources

## Performance of the system
Although the maps generated by our system provide valuable new information, they nevertheless contain substantial errors. The overall map accuracies are good (86.7-88%, Table \href{tab:mapaccuracy}), which is at the boundary of what could be considered achievable map accuracy [@ElmesAccountingtrainingdata2020], given the level of confidence in the map reference sample (only 85% of reference labels were assigned with confidence). However, accuracies for the cropland class were between 62 (Producer's) and 67 (User's) percent in the per-pixel map, indicating that both commission and omission errors were above 30% for this class. The field boundary has lower omission error (Producer's accuracy = 79%), but that comes at the expense of increased false positives (User's accuracy = 58.2%). These accuracies are near the middle to upper ranges of those reported for the cropland class in other large-area mapping studies [@hackmanNewLandcoverMaps2017; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]

@@

- Map at large scale using PlanetScope, one of the first (any citations). 
  - Done using small sat data for a single agricultural year, for two primary seasons
  - Follows recommended best practice for training ML algorithms

- Takes step towards answering important questions about the characteristics of fields and how many there are. 
  - Provide insights into the characteristics of croplands
  - Discussion about the characteristics of croplands: estimates of field sizes
  - What is says about Ghana's croplands.

## Performance of the system
- Pixel-wise system, reasonable overall accuracy, but low performance on the agricultural class
- Low performance primarily due to several factors:
  - Model simplicity and scale of compute
  - Challenge of labelling task - uncertainty in labels
    - Should also be noted substantial uncertainty in identifying fields (map reference uncertainty)
  - Difficulty of getting clean imagery in highly cloudy areas
- Design of system helped to mitigate these factors:
  - Consensus labels minimize error substantially
  - Active learning selects cites more efficiently, some evidence it improves more efficiently and overall relative to random selection. Less marked gain here, but doing this at much larger scale than Debats
  - Multi-season imagery helps improve it    
    - Feng et al (2020) importance of temporal information (backs up Debats et al).
    - temporal information makes labelling harder though
  - Image quality:
    - Developed our own mean-weighting not median composite (artifacts) (maybe methods)
    - impact on accuracy--residual cloud issues
    - Important to develop the method because best-on-top method of Planet's basemaps leaves lots of residual cloud in key seasons, and require large volumes of imagery in highly cloudy areas such as southerwestern Ghana.

- Segmentation accuracy issues:
  - Over-merging
  - Bias in mean sizes likely reflect agglomerations of contiguous smallholder fields, and the difficulty of segmenting indistinct adjacent boundaries. Such as in AOI 2,and the southern portion of AOI 8 (Figure S12A).
  - Importance of having high quality probabilities underlying for filtering segments

## Looking forward 
- Sets up capability for repeated annual mapping of croplands to understand critical issues of how these systems are changing (sizes and shapes of croplands, where they are expanding) (Jayne papers, recent agricultural expansion paper)
- Key components will be useful in other applications and regions
- Provides means for improving crop type and crop yield estimates
- Improvements to help realize these capabilities: promise of CNNs (cite Waldner paper, others), for segmentation to realize this. This systems is well designed to adapt to it, and capabilities for assessing various aspects of label quality, e.g. edge accuracy and fragmentation accuracy, can help improve quality of labels designed to emphasize edges
  - Can still retain the active architecture, but instead use new sites to improve a pre-trained model
- Map along agroecozone boundaries, rather than random blocks  
- Another interesting question to answer: whether guided approach to site selection would result in more informative sample for CNNs also.

>>>>

## Sources of error
Although the maps generated by our system provide valuable new information, they nevertheless contain substantial errors. The overall map accuracies are good (86.7-88%, Table \href{tab:mapaccuracy}), which is at the boundary of what could be considered achievable map accuracy [@ElmesAccountingtrainingdata2020], given the level of confidence in the map reference sample (only 85% of reference labels were assigned with confidence). However, accuracies for the cropland class were between 62 (Producer's) and 67 (User's) percent in the per-pixel map, indicating that both commission and omission errors were above 30% for this class. The field boundary has lower omission error (Producer's accuracy = 79%), but that comes at the expense of increased false positives (User's accuracy = 58.2%). These accuracies are near the middle to upper ranges of those reported for the cropland class in other large-area mapping studies [@hackmanNewLandcoverMaps2017; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]

These relatively low accuracies for the cropland class can be attributed to several important factors. The first of these was the overall mapping extent combined with the resolution of the analysis. Given the goal of country-scale mapping at high resolution, we found that the computational cost required us to use a relatively small and simple set of features and less than the recommended [@MaxwellImplementationmachinelearningclassification2018] tree number of depth  in our RandomForest implementation. Previous work shows that RandomForest achieves much better performance on small-scale croplands when trained on a large number of randomly generated features [@Debatsgeneralizedcomputervision2016], which is a commonality with deep learning. However, applying such a large feature set within the extent of our AOIs was intractable, as the computing time would have been several-fold larger than the typical 10-14 hours required from training through prediction on 800 CPUs, for a single iteration. This left the model less able to discern cropland from surrounding savanna vegetation with bare patches or sparse grass cover, which was common in most AOIs. A larger feature set with more variable textures filters could have helped distinguish such areas from crop fields, helping to particularly reduce commission error.

Another major limiting factor was the inherent difficulty of the labelling task. The system is designed to minimize the error inherent in labelling, but determining croplands from non-croplands over these system is difficult and requires educated guessing by each labeller. Interpretation is particularly hard over areas where the background savanna vegetation and croplands have similar reflectance during the dry season, which is a particular problem in AOIs 2 and 3. Such changes in scene circumstances require labellers to adopt different heuristics, for example by delineating the field boundary on the growing season rather than the dry season image. Smaller field sizes also complicated the labelling task, as smaller fields become increasingly indistinct in the ~4 m PlanetScope composites. These challenges caused substantial differences in labels, as evident in the Bayesian Risk metrics (Figure S5) and labeller accuracies that averaged 71%, as measured against our reference set. The design of our system allowed us to measure how much label quality impacts model performance. Although prior work [@mellorExploringIssuesTraining2015; @rodriguez-galianoAssessmentEffectivenessRandom2012] has reported that RandomForest is particularly robust to training data error, we found its impact to be substantial (Figure \href{fig:trainingimpact}), suggesting that the greatest single investment towards improved accuracy lies in improving training data quality.

Image quality was another issue, although primarily in the forest zone (Zone 4) AOIs, where frequent cloud cover reduced the number of available images in all seasons, resulting in composites with more brightness artifacts and blur (Figure \href{fig:imqual}). This impacted labellers' abilities to discern arable fields, and doubtless affected model predictions. There is little to be done to mitigate these errors, short of confining imagery to the less cloudy dry season, which may further undermine model performance--prior work shows that imagery from multiple seasons is important for improving classifier performance [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. Alternatively, composite quality could be improved by integrating imagery from the same seasons over multiple years, but this would undermine the goal of developing annual maps, while the dynamism of the croplands would confound the ability to delineate field boundaries. Alternative compositing approaches might also be ineffective, as the "best-on-top" approach\footnote{https://assets.planet.com/products/basemap/planet-basemaps-product-specifications.pdf} used to develop PlanetScope basemaps tends to result in substantial residual clouds in this region.

The final major error sources relates to the segmentation algorithm, which had two particular problems. The first of these relates to the substantial commission errors in the vector maps, which is attributable to errors in the RandomForest predictions. Uncertainty in that model resulted in substantial numbers of pixels just above the 0.5 classification threshold, meaning a number of segments over highly uncertain areas were retained as fields. This problem would resolve with a more accurate classifier, or potentially by using locally varying thresholds for distinguishing croplands from non-cropland [e.g. @waldnerDeepLearningEdge2020].  The second problem was over-merging by the segmentation algorithm, which caused over-estimation of field sizes and often irregular shapes, particularly in high density croplands, such as in AOIs 2 and 8 (Figure \href{fig:mainmap}), where closely adjacent small-scale fields have boundaries that are often indistinct in the PlanetScope imagery. In this case, minimizing or preventing merging could help, resulting in an over-segmented solution that would likely underestimate field sizes. However, from the standpoint of other map applications, such as filtering pixels for crop type mapping or yield estimation, over-segmented solutions could help by isolating distinct within field units, such as those caused by soil type differences.

## Key system features
- Design of system helped to mitigate these factors:
  - Consensus labels minimize error substantially
  - Active learning selects cites more efficiently, some evidence it improves more efficiently and overall relative to random selection. Less marked gain here, but doing this at much larger scale than Debats
  - Multi-season imagery helps improve it    
    - Feng et al (2020) importance of temporal information (backs up Debats et al).
    - temporal information makes labelling harder though
  - Image quality:

@@

## Looking forward 
- Provide new insight 
- Given errors, should be considered generation 1 maps
- Sets up capability for repeated annual mapping of croplands to understand critical issues of how these systems are changing (sizes and shapes of croplands, where they are expanding) (Jayne papers, recent agricultural expansion paper)
- Key components will be useful in other applications and regions
- Provides means for improving crop type and crop yield estimates
- Improvements to help realize these capabilities: 
-     [This suggests that replacing the Random Forest more advanced deep learning model]. promise of CNNs (cite Waldner paper, others), for segmentation to realize this. This systems is well designed to adapt to it, and capabilities for assessing various aspects of label quality, e.g. edge accuracy and fragmentation accuracy, can help improve quality of labels designed to emphasize edges
  - Can still retain the active architecture, but instead use new sites to improve a pre-trained model
- Map along agroecozone boundaries, rather than random blocks  
- Another interesting question to answer: whether guided approach to site selection would result in more informative sample for CNNs also.
- Higher number of high quality reference labels can achieve this.

# Suggested uses
- Fallow versus active
